\section{Chapter 0: Energy and Global Income Distribution}

\subsection{How is income distributed globally, and how does it relate to energy consumption?}
\solutionblock{}

\subsection{Compute the primary energy consumption in a fully developed country per capita and day from:}
\subsubsection{a) Estimating a person's individual consumption (heating, electricity, car, etc.)}
\solutionblock{}

\subsubsection{b) From the macroeconomic perspective of a whole country}
\solutionblock{}

\subsection{Explain energy intensity}
\solutionblock{}

\subsection{How do primary energy consumption and consumer electricity differ?}
\solutionblock{}

\subsection{What's the energy mix in Austria?}
\solutionblock{}

\subsection{Given a number for reserves of a single fossil resource, compute:}
\subsubsection{a) What part of the energy mix it can contribute sustainably (1000 years)}
\solutionblock{}

\subsubsection{b) How long would it last at current consumption levels}
\solutionblock{}

\subsection{How much W/m\textsuperscript{2} can various energy sources produce? How would you compute it?}
\solutionblock{}

\subsection{Discuss whether renewables compete with arable land for food production. What about biofuels?}
\solutionblock{}

\subsection{Discuss the ongoing price-drop in solar, and what it means for other alternatives, such as future fusion energy}
\solutionblock{}

\subsection{Discuss the question of perceived and quantitative risk for the environment from various aspects of civilization (e.g., birds vs cats/wind turbines)}
\solutionblock{}

\subsection{Are there CO\textsubscript{2}-free energy sources? Why/why not?}
\solutionblock{}
