\section{Chapter 2: Discoveries Leading to Fusion}

\subsection{Give a historical perspective on the scientific discoveries that led to the discovery of fusion.}
\solutionblock{In Keywords: \\
1) $E = m \cdot c^2$: Probably one of the most important formulas in physics.\\
2) Einsteins equivalence of mass and energy led to the concept of fusion energy. \\
3) Francis Aston invented mass spectroscopy and measured that Helium is lighter than 4 Hydrogen atoms. (also explained Isotopes). Eddington realized that Francis measurements mean, that stars convert mass to energy.\\
4) James Chadwick discovered the neutron which could explain isotopes in 1932.\\
5) Bonding force in nucleus is given by the mass defect - the difference between the mass of the nucleus and the sum of the masses of the protons and neutrons.\\
6) Otto Hahn and Fritz Strassmann discovered nuclear fission of uranium by bombarding it with neutrons.\\
7) In 1939 Lise Meitner and Otto Frisch discovered that the nucleus of Uranium splits into two lighter nuclei and that the mass defect is converted to energy.\\
8) In 1942 Enrico Fermi built the first nuclear reactor.\\
9) In 1945 the first atomic bomb was detonated.\\
}

\subsection{Explain how the mass defect of various isotopes can be used to extract energy in fission and fusion.}
\solutionblock{Free neutrons and protons have slightly more mass than neutrons and protons in a nucleus. The difference in mass is called the mass defect. The mass defect is converted to energy when the nucleus is formed - this energy is called binding energy.\\
In fission the mass defect is converted to energy when the nucleus splits into two lighter nuclei. Fission releases energy for nuclei heavier than Iron and fusion releases energy for nuclei lighter than Iron.\\}
